Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
Add reponse to question about model comparison.

In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f \diff V$, where $\gamma$ is a factor
representing heat dissipation by gamma and neutron irradiation in the moderator,
called the graphite to fuel power density ratio. \cite{robertson_conceptual_1971}'s
original \gls{MSBR} analysis included a calculation of $\gamma$.
\cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011} all
calculated gamma heating through such a factor. We follow \cite{cammi_multi-physics_2011}
and set $\gamma=0.0144$. Notably, the Moltres physics kernel for radiation heating can be
calculate the volume average fission heat in a variety of means: whole-core and local averages
are possible. Whole-core averages are employed for simplicity and in accordance with prior literature.
Knowledge of fision heat rates, however, require knowledge of neutron fluxes, implying a need for
group constants.

@@

The profile shapes are in decent qualitative agreement with both Moltres and
\gls{MSRE} calculations showing a peak in graphite temperature before the
reactor outlet. Fuel temperature increases monotonically in both Moltres and
\gls{MSRE} models. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 20 degrees Fahrenheit larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

@@

>>>>

In this work, $Q_g = \gamma V_{\text{core}}^{-1} \int_{\text{core}}Q_f \diff V$, where $\gamma$ is a factor
representing heat dissipation by gamma and neutron irradiation in the moderator,
called the graphite to fuel power density ratio. Robertson's \cite{robertson_conceptual_1971}
original \gls{MSBR} analysis included a calculation of $\gamma$.
\cite{krepel_dyn3d-msr_2007,zhang_development_2009,cammi_multi-physics_2011} all
calculated gamma heating through such a factor. We follow \cite{cammi_multi-physics_2011}
and set $\gamma=0.0144$. Notably, the Moltres physics kernel for radiation heating can be
calculate the volume average fission heat in a variety of means: whole-core and local averages
are possible. Whole-core averages are employed for simplicity and in accordance with prior literature.
Knowledge of fision heat rates, however, require knowledge of neutron fluxes, implying a need for
group constants.

@@

The profile shapes are in decent qualitative agreement with both Moltres and
\gls{MSRE} calculations showing a peak in graphite temperature before the
reactor outlet. Fuel temperature increases monotonically in both Moltres and
\gls{MSRE} models. In the \gls{MSRE} design, the moderator
temperature at the reactor inlet is about 11 K larger than the
fuel temperature, whereas the temperatures are about the same in the Moltres
model. This difference is likely because the \gls{MSRE} design model
neglected axial heat conduction \cite[p. 99]{briggs_molten-salt_1964}.

@@

Although the qualitative agreement is decent, there are discrepancies between
the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
the hottest channel. The peak graphite temperature is around 14 K larger in the
Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
roughly 20\%. These are not insignificant differences. However, given the
differing nature of the two models--no axial conduction in the \gls{MSRE} model,
2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
Moltres calculation--we believe this variation in quantitative behavior is
acceptable for the purpose of this work, which is to introduce Moltres as a
simulation tool. Trustworthy verification of Moltres results, such as spatial flux
and temperature profiles, will require more detailed experimental measurements
than those available in the \gls{ORNL} technical reports, which contain only
macroscopic data such as steady-state power and heat-exchanger temperature
drops. Additionally, detailed comparison with other modern modeling efforts such
as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
desirable. In that vein, a collaboration is under way with the primary author of
\cite{aufiero_develoment_2014} to try and reproduce calculation results from
OpenFOAM. We hope to publish the results of this comparison in a future work.

### 2017-11-27 revise/revise.tex
Add reponse to question about model comparison.

\question The differences between the MSRE and the Moltres model are significant
and should be discussed in more details. In particular the difference between
fast fluxes is suspicious.
\begin{solution}
        <++>
\end{solution}

>>>>

\question The differences between the MSRE and the Moltres model are significant
and should be discussed in more details. In particular the difference between
fast fluxes is suspicious.
\begin{solution}
        We have added the following passage at the end of the comparison section
        to address this concern:

        Although the qualitative agreement is decent, there are discrepancies between
        the \gls{MSRE} and Moltres calculations. As outlined above there is an 11 K
        offset between \gls{MSRE} and Moltres calculations for the fuel temperature in
        the hottest channel. The peak graphite temperature is around 14 K larger in the
        Moltres calculation. Fast fluxes are larger in the \gls{MSRE} calculation by
        roughly 20\%. These are not insignificant differences. However, given the
        differing nature of the two models--no axial conduction in the \gls{MSRE} model,
        2-group vs 32-group neutronics, exclusion of the control rod thimbles in the
        Moltres calculation--we believe this variation in quantitative behavior is
        acceptable for the purpose of this work, which is to introduce Moltres as a
        simulation tool. Trustworthy verification of Moltres results, such as spatial flux
        and temperature profiles, will require more detailed experimental measurements
        than those available in the \gls{ORNL} technical reports, which contain only
        macroscopic data such as steady-state power and heat-exchanger temperature
        drops. Additionally, detailed comparison with other modern modeling efforts such
        as that conducted in \cite{aufiero_development_2014,laureau_transient_2017} is
        desirable. In that vein, a collaboration is under way with the primary author of
        \cite{aufiero_develoment_2014} to try and reproduce calculation results from
        OpenFOAM. We hope to publish the results of this comparison in a future work.
\end{solution}
